Open-source landscape for 3D CSEM modelling

### 2020-05-05 manuscript/Manuscript.tex

% Remove once done
\newcommand{\mycom}[2][]{
  \todo[]{\textbf{\uppercase{[#1]}}:~#2}}
\newcommand{\imycom}[2][]{
  \todo[inline]{\textbf{\uppercase{[#1]}}:~#2}}
\newcommand{\dul}[1]{\underline{\underline{#1}}}
\newcommand{\ul}[1]{\underline{#1}}
\newcommand{\rmk}[1]{{\color{red}{#1}}}
\newcommand{\ohmm}{\ensuremath{\Omega\,}\text{m}\xspace}

@@

\imycom[DW]{
  For comments in the margin, use:\\[.2cm]
  \qquad\texttt{\textbackslash mycom[YOURINITIALS]\{comment\}}\\[.2cm]
  and for inline comments, use:\\[.2cm]
  \qquad\texttt{\textbackslash imycom[YOURINITIALS]\{comment\}}
}

\imycom[DW]{
We will have to decide on a Journal. Current suggestions:\\
- GMD: Geoscientific Model Development\\
- SIG: Surveys in Geophysics\\
- SE: Solid Earth\\
- GJI: Geophysical Journal International\\
- GP: Geophysical Prospecting\\
- GEO: Geophysics\\
- CAG: Computers and Geosciences\\
I think \emph{Geoscientific Model Development} and \emph{Surveys in Geophysics}
were the favourite ones when we discussed it ones. I personally would be very
interested in GMD. What do you think? But also interesting would be the GJI,
because the MT comparison was published there, so it would be in the same
place.
}

@@

It is this topic that we address, open-source 3D CSEM codes. Some major
exploration service companies as well as certain research consortia and
research groups have their 3D CSEM codes. But how about codes that are
open-source? Research code was traditionally often available upon request by
the author. Codes distributed that way often come with the request to not share
the code, and they often come without a license attached at all (which means
that they are not open-source). Also, at times there can be significant hurdles
to install a code. However, the meaning of open-source evolved rapidly in the
last decades. Today, open-source generally not only means that a code is
available (with a proper license). The meaning includes much more these days,
such as that the code is hosted online, is under version control, has the
possibility to file issues and make pull requests to fix bugs. Well maintained
codes often have continuous integration that includes testing of the code base
and online hosted documentation which often includes code documentation,
examples, and tutorials. As such the term has shifted from purely open-source
code to development in the open and increasingly building a global community.
There are a number of projects within the realm of geophysical exploration,
besides the ones we present here, \todo{Others coming to your mind?}e.g.
pyGIMLi \citep{CAG.17.Rucker} and Fatiando \citep{JOSS.18.Uieda}. Newer
\todo{wrong term, think about it}programming environments  have also brought
much simplifications in the installation process and have most importantly
simplified it for code developers to make their codes easily available and
installable. All our presented codes are in the Python ecosystem, and each code
can be installed with a single command (which includes downloading and
installation).

@@

It is worth mentioning that there are many more 3D EM codes developed in other
fields than geophysics such as communication systems (antennas, radar,
satellites), medical imaging. There are various open-source codes in these
fields \todo{Add at least three references} too, e.g., Elmer
(\href{http://www.csc.fi/elmer}{csc.fi/elmer}, couldn't find a publication,
just a poster). While these codes could potentially be used for the same goals
as presented here we restrict our review to codes purpose-built, and ready
without further adjustments, for geophysical applications.

@@

\tabl[btp]{codecomparison}{All codes solve the weak form of Maxwell's equations
  in its differential form (DE) under the quasistatic approximation. Note that
  \emg3d is a solver on its own, while the other codes implement third-package
  solvers such as \texttt{PETSc}, \texttt{MUMPS}, or \texttt{PARDISO}
  \citep{FGCS.04.Schenk}.
  \imycom[DW]{\texttt{PETSc} and \texttt{MUMPS} probably need citations too.}
}{
  \centering
  \footnotesize
\begin{tabularx}{\linewidth}{lXXXX}
  \toprule
  %
  & \custem & \emg3d & \petgem & \simpeg  \\
  \midrule
  %
  Home & \href{https://custem.rtfd.io}{custem.rtfd.io}
       & \href{https://empymod.github.io}{empymod.github.io}
       & \href{http://petgem.bsc.es}{petgem.bsc.es}
       & \href{https://docs.simpeg.xyz}{simpeg.xyz} \\
  License & GPL-3.0 & Apache-2.0 & GPL-3.0 & MIT \\
  Installation & \texttt{pip}; \texttt{conda}
               & \texttt{pip}; \texttt{conda}
               & \texttt{conda}
               & \texttt{pip}; \texttt{conda} \\
  Comp. Dom. & frequency \& time & frequency & frequency & frequency \& time \\
  Method & FE & FV & FE & FV \\
  Mesh & tetrahedral & rectilinear & tetrahedral & recti- \& curvilinear \\
  BC & PMC; PEC & PEC & PEC & PEC; PMC \\
  Solver & \texttt{MUMPS} & \emg3d & \texttt{PETSc}; \texttt{MUMPS} &
           \texttt{PARDISO}; \texttt{MUMPS} \\
  %
  \bottomrule
\end{tabularx}}%
%

@@

\imycom[DW]{
Each code should be briefly summarized by three points:\\
- Brief intro\\
- Main selling point\\
- Planned features\\
I think in a first round \textbf{everyone should just write what they want to
write and think is important for their code}. In a second round we should then
homogenize it, such that all codes have more or less the same length/weight and
also similar topic/layout.
}

@@

TODO (\texttt{FEniCS}; \cite{CSE.15.Alnaes})

@@

The 3D CSEM modeller \emg3d is a multigrid \citep{CMMP.64.Fedorenko} solver for
3D electromagnetic diffusion following \cite{GP.06.Mulder}, with tri-axial
electrical anisotropy, isotropic electric permittivity, and isotropic magnetic
permeability. The matrix-free solver can be used as main solver or as
preconditioner for one of the Krylov subspace methods implemented in SciPy, and
the governing equations are discretized on a staggered grid by the
finite-integration technique \citep{AEU.77.Weiland}, which is a finite-volume
generalization of a Yee grid. The code is written completely in Python using
the NumPy and SciPy stacks, where the most time- and memory-consuming parts are
sped up through jitted (just-in-time compiled) functions using Numba
\citep{LLVM.15.Lam}. The code computes the electric field due to an electric
source in the frequency-domain. Implemented are functions to obtain the
magnetic field due to an electric source; to obtain the electric and magnetic
fields due to a magnetic source; and to obtain time-domain responses.

The multigrid method is characterized by almost linear scaling both in terms of
runtime (CPU) and memory (RAM) usage, and it is therefore a comparably
low-memory consumption solver. It is also minimal in terms of requirements,
only NumPy, SciPy, and Numba are required, with Python 3.7+. The current
development is focused on adding inversion capabilities. A further plan is also
to implement a hook in order to use \emg3d as a solver within the \simpeg
framework.

@@

The difference becomes only significant at offsets larger than 8\,km. However,
this is due to a practical difference in the meshing: This simple block model
is advantageous for FV codes, as it consists of rectangular blocks and
horizontal layers, simple geometric objects. While having a very thin, shallow
layer is straight-forward for FV codes, it requires many cells for a FE code.
The thin layer was therefore limited in its horizontal extent
to\mycom[DW]{Raphael, to what x/y?} ???. This is the reason for the increased
NRMSD at large offsets, and it has nothing to do with the accuracy of the
computation itself.

@@

\imycom[DW]{Next:\\
  - Create figures for Marlim\\
  - Write text for Marlim\\
  - Discussion\\
  - Conclusions\\
  - Send to Raphael
}

The Marlim R3D model is a \dots \cite{BJG.17.Carvalho} (model)
\cite{GEO.19.Correa} (CSEM data)

Comparison to an code from the industry, using \emph{SBLwiz} from EMGS.

Custom meshes for these lines.

%
\tabl[btp]{comp-marlim}{Comparison of used CPU and RAM and of number of cells
  used to discretize the Marlim R3D model. \imycom[DW]{I will fill this table
  out once we all submitted the final versions of the results.}}{
  \centering
\begin{tabular}{lS[table-format=4.2]rS[table-format=4.2]rl}
  \toprule
  %
  Code & {CPU} & \#Procs & RAM     & \#Cells \\
       & {(s)} &         & {(GiB)} &         \\
  \midrule
  %
  \custem & 0.0 & 24 & 0.0 & 0 \\
  \emg3d  & 0.0 &  1 & 0.0 & 0 \\
  \petgem & 0.0 & 48 & 0.0 & 0 \\
  \simpeg & 0.0 &    & 0.0 & 0 \\
  %
  \bottomrule
\end{tabular}}%
%

\clearpage  % TODO: Just for now while drafting, remove later!
\section{Discussion}

=> \textbf{Important point: Verification of existing and future codes: this is
a start!}

@@

Points to discuss and mention
\begin{itemize}
  \item Direct solvers vs indirect solvers, both its advantages and
    disadvantages; memory, various sources.
\end{itemize}

\dots

Here we only consider frequency-domain results from frequency-domain
computations. Similar comparison for time-domain results from time-domain
computations, and frequency-domain results from time-domain computations and
vice versa using Fourier transforms would also be good.

The readily availability of many codes means there will be many more people
able to model 3D results, and not just a few specialists in the field. Whilst
this is amazing and will push the field much further it also means that the
same mistakes might happen over and over again, and comparisons and examples
like these can help to avoid this.

\subsection{Future (?)}

Comment KK: \emph{One thing that the community could really use is more test
models for various scenarios, and having them be easily accessible.}

\subsection{MARE3DEM}

This is, I thought, the right spot where Kerry Key could write a bit about
MARE3DEM, if (and I think only if) there are clear plans and a time-scale to
open-source it. Embedded in a wider summary of available codes (some research
required).

\clearpage  % TODO: Just for now while drafting, remove later!
\section{Conclusions}

The landscape in 3D CSEM modelling greatly changed in the last five years or
so. While before there were only closed-source codes owned by companies or
consortia there was recently a wave of openly released codes.

Results from numerical modellers for simple models, such as a halfspace below
air or a sphere in a fullspace, can be verified by comparing them to analytical
solutions. However, there is no such possibility for complicated, realistic
models. The only way to gain confidence in numerical results is by comparing
different codes to each other. We hope that our efforts help to the confidence
in the available open-source codes\dots

@@

It is important to note that there exist many more 3D electromagnetic codes
from various fields, such as civil engineering or medicine, in Python and in
many other languages (list a few references here). Here we focused on codes in
Python developed for geophysical exploration.

\dots

@@

All files to rerun the different models with the four codes and reproduce the
shown results are available at \todo{zenodo}\dots.

>>>>

% Remove once done
\newcommand{\mycom}[2][]{
  \todo[color=yellow]{\textbf{\uppercase{[#1]}}:~#2}}
\newcommand{\imycom}[2][]{
  \todo[inline, color=yellow]{\textbf{\uppercase{[#1]}}:~#2}}
\newcommand{\itodo}[1]{\todo[inline, color=cyan]{\sffamily #1}}
\newcommand{\dul}[1]{\underline{\underline{#1}}}
\newcommand{\ul}[1]{\underline{#1}}
\newcommand{\rmk}[1]{{\color{red}{#1}}}
\newcommand{\ohmm}{\ensuremath{\Omega\,}\text{m}\xspace}

@@

\itodo{
  For comments in the margin, use:\\[.2cm]
  \qquad\texttt{\textbackslash mycom[YOURINITIALS]\{comment\}}\\[.2cm]
  and for inline comments, use:\\[.2cm]
  \qquad\texttt{\textbackslash imycom[YOURINITIALS]\{comment\}}
}

\itodo{
We will have to decide on a Journal. Current suggestions:\\
- GMD: Geoscientific Model Development\\
- SIG: Surveys in Geophysics\\
- SE: Solid Earth\\
- GJI: Geophysical Journal International\\
- GP: Geophysical Prospecting\\
- GEO: Geophysics\\
- CAG: Computers and Geosciences\\
I think \emph{Geoscientific Model Development} and \emph{Surveys in Geophysics}
were the favourite ones when we discussed it ones. I personally would be very
interested in GMD. What do you think? But also interesting would be the GJI,
because the MT comparison was published there, so it would be in the same
place. I just had a very bad experience with GP, so I am not inclined on that
at all.
}

@@

It is this topic that we address, open-source 3D CSEM codes. Some major
exploration service companies as well as certain research consortia and
research groups have their 3D CSEM codes. But how about codes that are
open-source? Research code was traditionally often available upon request by
the author. Codes distributed that way often come with the request to not share
the code, and they often come without a license attached at all (which means
that they are not open-source). Also, at times there can be significant hurdles
to install a code. However, the meaning of open-source evolved rapidly in the
last decades. Today, open-source generally not only means that a code is
available (with a proper license). The meaning includes much more these days,
such as that the code is hosted online, is under version control, has the
possibility to file issues and make pull requests to fix bugs. Well maintained
codes often have continuous integration that includes testing of the code base
and online hosted documentation which often includes code documentation,
examples, and tutorials. As such the term has shifted from purely open-source
code to development in the open and increasingly building a global community.
There are a number of projects within the realm of geophysical exploration,
besides the ones we present here, \mycom[DW]{Others coming to your mind?}e.g.
pyGIMLi \citep{CAG.17.Rucker} and Fatiando \citep{JOSS.18.Uieda}. Newer
\mycom[DW]{wrong term, think about it}programming environments  have also
brought much simplifications in the installation process and have most
importantly simplified it for code developers to make their codes easily
available and installable. All our presented codes are in the Python ecosystem,
and each code can be installed with a single command (which includes download
and installation).

@@

It is worth mentioning that there are many more 3D EM codes developed in other
fields than geophysics such as communication systems (antennas, radar,
satellites), medical imaging, or civil engineering. There are various
open-source codes in these fields too, e.g., Elmer \mycom[DW]{Add 2-3 proper
references} (\href{http://www.csc.fi/elmer}{csc.fi/elmer}, couldn't find a
publication, just a poster). While these codes could potentially be used for
the same goals as presented here we restrict our review to codes purpose-built,
and ready without further adjustments, for geophysical applications.

@@

\tabl[btp]{codecomparison}{All codes solve the weak form of Maxwell's equations
  in its differential form (DE) under the quasistatic approximation. Note that
  \emg3d is a solver on its own, while the other codes implement third-package
  solvers such as \texttt{PETSc} \citep{Preprint.Abhyankar}, \texttt{MUMPS}
  \citep{SIAM.01.Amestoy}, or \texttt{PARDISO} \citep{FGCS.04.Schenk}.
}{
  \centering
  \footnotesize
\begin{tabularx}{\linewidth}{lXXXX}
  \toprule
  %
  & \custem & \emg3d & \petgem & \simpeg  \\
  \midrule
  %
  Home & \href{https://custem.rtfd.io}{custem.rtfd.io}
       & \href{https://empymod.github.io}{empymod.github.io}
       & \href{http://petgem.bsc.es}{petgem.bsc.es}
       & \href{https://docs.simpeg.xyz}{simpeg.xyz} \\
  License & GPL-3.0 & Apache-2.0 & GPL-3.0 & MIT \\
  Installation & \texttt{pip}; \texttt{conda}
               & \texttt{pip}; \texttt{conda}
               & \texttt{conda}
               & \texttt{pip}; \texttt{conda} \\
  Comp. Dom. & frequency \& time & frequency & frequency & frequency \& time \\
  Method & FE & FV & FE & FV \\
  Mesh & tetrahedral & rectilinear & tetrahedral & recti- \& curvilinear \\
  BC & PMC; PEC & PEC & PEC & PEC; PMC \\
  Solver & \texttt{MUMPS} & \emg3d & \texttt{PETSc}; \texttt{MUMPS} &
           \texttt{PARDISO}; \texttt{MUMPS} \\
  %
  \bottomrule
\end{tabularx}}%
%

@@

\itodo{
Each code should be briefly summarized by three points:\\
- Brief intro\\
- Main selling point\\
- Planned features\\
I think in a first round \textbf{everyone should just write what they want to
write and think is important for their code}. In a second round we should then
homogenize it, such that all codes have more or less the same length/weight and
also similar topic/layout.
}

@@

@@

The 3D CSEM modeller \emg3d is a multigrid \citep{CMMP.64.Fedorenko} solver for
3D electromagnetic diffusion following \cite{GP.06.Mulder}, with tri-axial
electrical anisotropy, isotropic electric permittivity, and isotropic magnetic
permeability. The matrix-free solver can be used as main solver or as
preconditioner for one of the Krylov subspace methods implemented in SciPy, and
the governing equations are discretized on a staggered grid by the
finite-integration technique \citep{AEU.77.Weiland}, which is a finite-volume
generalization of a Yee grid. The code is written completely in Python using
the NumPy and SciPy stacks, where the most time- and memory-consuming parts are
sped up through jitted (just-in-time compiled) functions using Numba
\citep{LLVM.15.Lam}. The code computes the electric field due to an electric
source in the frequency-domain, which is its main application (frequency-domain
CSEM). However, there are also routines to obtain the magnetic field due to an
electric source, to obtain the electric and magnetic fields due to a magnetic
source, and to obtain time-domain responses.

The multigrid method is characterized by almost linear scaling both in terms of
runtime (CPU) and memory (RAM) usage, and it is therefore a comparably
low-memory consumption solver. It is also minimal in terms of requirements,
only NumPy, SciPy, and Numba are required, with Python 3.7+. The current
development is focused on adding basic inversion capabilities, and a further
plan is to implement a hook in order to use \emg3d as a frequency-domain CSEM
solver within the grander \simpeg framework.

@@

The difference becomes only significant at offsets larger than 8\,km. However,
this is due to a practical difference in the meshing: This simple block model
is advantageous for FV codes, as it consists of rectangular blocks and
horizontal layers, simple geometric objects. While having a very thin, shallow
layer is straight-forward for FV codes, it requires many cells for a FE code.
The thin layer was therefore limited in its horizontal extent
to\mycom[DW]{Raphael, to what x/y exactly?} ???. This is the reason for the
increased NRMSD at large offsets, and it has nothing to do with the accuracy of
the computation itself.

@@

The Marlim oil field is a giant reservoir in a turbidite sandstone horizon in
the north-eastern part of the Campos Basin, offshore Brazil, which was
discovered in 1985. \cite{BJG.17.Carvalho} created from seismic data and well
log data a realistic resistivity model with vertical transverse isotropy (VTI),
Marlim R3D (MR3D), which they released under an open-source license. Using this
model \cite{GEO.19.Correa} computed CSEM data for six frequencies from
0.125\,Hz to 1.25\,Hz, which they also released under an open-source license.
To compute the data they used a state-of-the-art code from the industry
\citep{GEO.07.Maao}. It is therefore an ideal case to verify our open-source
codes against, as it is a complex, realistic model, and the data were computed
by an industry-proofed code. Additionally, that code is a time-domain code,
whereas the four codes under consideration here compute the results all in the
frequency-domain.

The detailed reservoir model consists of 1022 by 371 by 1229 cells, totalling
to almost 466 million cells, where each cell has dimensions of 25 by 75 by
5\,m. For the computation the model is upscaled to 515 by 563 by 310 cells,
totalling to almost 90 million cells, where each cell has dimensions of 100 by
100 by 20\,m.

The published data set consists of a regular grid of receivers of 20 in
eastern direction by 25 in northern direction, 500 receivers in total, with
1\,km spacing located on the irregular seafloor. 45 source-towlines were
located on the same grid, 50\,m above the seafloor, with shots every 100\,m. In
\cite{GEO.19.Correa} the actual responses for one receiver with the
corresponding East-West inline and one East-West broadside acquisition line are
shown, which is the data we chose for our comparison. The cross-section of the
resistivity model along the chosen inline acquisition line is shown in
Figure~\ref{fig:model-marlim}, together with the acquisition information.
%
\plot*{model-marlim}{width=\textwidth}{
  This figure obviously needs to be improved massively (at least a colorbar).
  What would you like to show from the actual data here?
  A nice figure would  be Figure 2 in \cite{GEO.19.Correa}; however, note that
  the drawn survey line in that figure are plainly wrong. If someone is
  familiar with GMT and happy to make a make that would be great. Also, the
  cross-section is currently heavily vertically exaggerated.
}
%

We computed all all six frequencies for all components ($E_x$, $E_y$, $E_z$)
for both inline and broadside acquisition lines. However, we show here only
the three frequencies and the responses with the strongest amplitudes (which
are generally used in processing), which are $E_x$ inline and broadside and
$E_y$ broadside. The comparison is shown in Figure~\ref{fig:results-marlim}.
%
\plot*{results-marlim}{width=\textwidth}{
  This is one heck of a figure. Just an idea, please make suggestions how to
  improve it (currently, \petgem data is a copy of \custem data, and \simpeg
  data is a copy of \emg3d data).
}
%

\imycom[DW]{There are some interesting features we should highlight. But again,
we first need all results. E.g.}
\begin{itemize}
  \item 0.125\,Hz: on the left side, \custem and \emg3d are almost identical,
    but very different from MR3D. So there I actually trust more our
    calculation, or there is a difference in the model that we did not take
    into account.
  \item 0.125\,Hz: on the right side, \custem is very similar to MR3D, whereas
    \emg3d is off.
  \item 0.125\,Hz and 0.5\,Hz: on the right side, \custem seems to very similar
    to MR3D.
\end{itemize}

%
\tabl[btp]{comp-marlim}{Comparison of used CPU and RAM and of number of cells
  used to discretize the Marlim R3D model. \imycom[DW]{I will fill this table
  out once we all submitted the final versions of the results.}}{
  \centering
\begin{tabular}{lS[table-format=4.2]rS[table-format=4.2]rl}
  \toprule
  %
  Code & {CPU} & \#Procs & RAM     & \#Cells \\
       & {(s)} &         & {(GiB)} &         \\
  \midrule
  %
  \custem & 0.0 &  0 & 0.0 & 0 \\
  \emg3d  & 0.0 &  0 & 0.0 & 0 \\
  \petgem & 0.0 &  0 & 0.0 & 0 \\
  \simpeg & 0.0 &  0 & 0.0 & 0 \\
  %
  \bottomrule
\end{tabular}}%
%

\clearpage  % TODO: Just for now while drafting, remove later!
\section{Discussion}
%
% enago.com/academy/discussion-conclusion-know-difference-drafting-manuscript/
%
% In order to make your discussion section engaging, you should include the
% following information:
% - The major findings of your study
% - The meaning of those findings
% - How these findings relate to what others have done
% - Limitations of your findings
% - An explanation for any surprising, unexpected, or inconclusive results
% - Suggestions for further research
%
% Your discussion should NOT include any of the following information:
% - New results or data not presented previously in the paper
% - Unwarranted speculation
% - Tangential issues
% - Conclusions not supported by your data
%

\imycom[DW]{Maybe we should create a Google-Doc for working on the Discussion
collaboratively at the same time?}

We compared four different, open-source 3D CSEM modellers by computing
responses for (a) a layered, anisotropic model without and with three resistive
blocks, and (b) a realistic 3D model. The comparison shows that the codes do
yield the same responses. As such we could verify the accuracy of these four
codes.

This is a very important insight. The possibilities to verify the accuracy of
3D CSEM codes are limited. One can compare them to analytical and
semi-analytical solutions, but they only exist for very simple models. For
complex models comparisons to other codes is the only possibility.
It is therefore really important to have more test models, and importantly, for
various scenarios, and that they are easily accessible. Our data should also
make it very easy for new codes to have a readily available data set to test
against and verify.

A similar exercise has be done for magnetotelluric (MT) 3D modelling and
inversion by \cite{GJI.13.Miensopust}, but we are not aware of anything like
this for CSEM data. However, we do hope that more comparisons will emerge in
the future, particularly with the current increase in open-source codes as well
as open-source data.

The codes under consideration consisted of finite element and finite
differences. However, it has to be noted that the chosen models are better
suited for finite differences codes. The first model for obvious reasons, as it
is a layered background containing blocks, all aligned in Cartesian
coordinates. The second model, Marlim R3D, could be an ideal case for FE codes,
as it comes with lithological horizons from seismic data. However, the
corresponding, published resistivity model uses a Cartesian grid. An extension
of this work could be to use a complex model tailored for a FE code, and
compare how the FD codes cope with it.

The codes under consideration use direct and indirect solvers, \dots blabla say
something. Having calculated in each model only one source favours in the
runtime comparison the iterative solver and therefore \emg3d. For the iterative
solvers additional sources would come at almost no cost, whereas for \emg3d it
would come at the same cost as the first source. This is something to keep in
mind when choosing the appropriate modeller for a problem at hand.

\imycom[DW]{I would like to capture as many as possible of the (I) differences,
(II) difficulties, (III) advantages, and (IV) disadvantages, that we
encountered in this exercise. This includes differences from direct to
iterative solver and differences from FE to FD codes etc. Please just jot down
things that come to your mind.}

Finally, the comparison in our study is limited to marine CSEM cases in the
frequency-domain. We hope that similar studies will be carried out for land
CSEM data and for time-domain data as well.

\clearpage  % TODO: Just for now while drafting, remove later!
\section{Conclusions}
%
% enago.com/academy/discussion-conclusion-know-difference-drafting-manuscript/
%
% Your conclusion should:
% - Restate your hypothesis or research question
% - Restate your major findings
% - Tell the reader what contribution your study has made to the existing
%   literature
% - Highlight any limitations of your study
% - State future directions for research/recommendations
%
% Your conclusion should NOT:
% - Introduce new arguments
% - Introduce new data
% - Fail to include your research question
% - Fail to state your major results
%

\imycom[DW]{Maybe we should create a Google-Doc for working on the Conclusions
collaboratively at the same time?}

\imycom[DW]{I obviously haven't really done this section, just af few thoughts
that I noted over time. I think the discussion (as the abstract) has to be
tackled once the rest is at least in a draft status and all data is ready.}

@@

What is missing for these emerging codes is a comparison and verification
suite, test models beyond the usual, analytical fullspace and halfspace models
and the semi-analytical layered Earth models. We hope that our efforts help to
the confidence in the available open-source codes\dots

@@

@@

All files to rerun the different models with the four codes and reproduce the
shown results are available at \dots.
\itodo{Put up on Zenodo, link here.}
